Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-09 manuscript/paper.Rmd
up

In order to select variables impacting blood pressure, we proceed by
doing some variable selection with regularization techniques. We first
employ best subset selection by using 10-fold cross validation to select
the best number of subsets. For syastolic blood pressure, forward best
subset selection choose 13 variables and for diastolic blood pressure 19
variables. These variables are showed, along with its significance in
Table \@ref(tab:tabreg)

```{r tabref, echo=FALSE}
tab.ref %>% as_kable_extra(booktabs = T, caption ="Coefficients for Foward Best Subset Selection") %>% kable_styling(latex_options = "scale_down")

@@

# Discussion and conclusion

>>>>

With the purpose of identifying influential variables impacting blood
pressure, a variable selection process was conducted. The initial
approach involved employing best subset selection with 10-fold
cross-validation to ascertain the optimal number of subsets. Notably,
for systolic blood pressure, the forward best subset selection method
discerned 13 variables, whereas diastolic blood pressure exhibited 19
selected variables. However, a limitation inherent in forward best
subset selection is its inability to eliminate previously selected
features, potentially disregarding their relevance in light of newly
added variables. Consequently, this methodology may yield suboptimal
variable selections due to its lack of adaptability.

In an effort to mitigate this limitation and introduce regularization,
LASSO regularization was employed. This involved a 10-fold
cross-validation process to determine the optimal penalty parameter,
$\lambda$ . For diastolic blood pressure, the $\lambda$ value associated
with the lowest mean squared error (MSE) led to the selection of 25
variables. Conversely, when considering systolic blood pressure, the
$\lambda$ value minimizing the MSE resulted in the exclusion of a sole
variable. Subsequently, a $\lambda$ value was strategically chosen to
ensure a negligible increase of no more than 1% in MSE, ultimately
leading to the inclusion of 29 variables in the model.

@@

### Foward Stepwise Best Subset

```{=tex}
\begin{align*}
\text{sbp} = &\, 85.65 + 0.47 \times \text{BMI} + 1.49 \times \text{total\_chol} - 0.00 \times \text{creatinine} \\
&+ 3.06 \times \text{educ\_levelHighschool} + 2.00 \times \text{educ\_levelLess12grade} + 1.31 \times \text{educ\_levelsomCollege} \\
&+ 4.59 \times \text{genderMale} + 0.47 \times \text{age\_yr} + 2.05 \times \text{marital\_statusLiving with partner} \\
&- 0.12 \times \text{marital\_statusMarried} + 3.30 \times \text{marital\_statusNever married} \\
&- 0.99 \times \text{marital\_statusSeparated} + 7.01 \times \text{marital\_statusWidowed} - 1.30 \times \text{sleep>8hrs} \\
&- 2.82 \times \text{sleep6-8hrs} - 4.60 \times \text{raceMexican American} - 3.78 \times \text{raceOther} \\
&- 5.03 \times \text{raceWhite income\_categoryLower-middle income} - 3.02 \times \text{income\_categoryMiddle income} \\
&- 2.88 \times \text{income\_categoryUnknown/Refused} - 2.70 \times \text{income\_categoryUpper-middle income} \\
&- 4.30 \times \text{income\_categoryVaried/High income}
\end{align*}
```
```{=tex}
\begin{align*}
\text{dbp} = &\, 53.55 + 0.22 \times \text{BMI} + 0.78 \times \text{total\_chol} + 0.85 \times \text{hemoglobin} + 0.02 \times \text{albumin} \\
&+ 0.03 \times \text{AST} - 0.89 \times \text{diabetesNo} - 3.37 \times \text{diabetesYes} - 1.06 \times \text{children..51} \\
&- 1.67 \times \text{children..52} - 1.83 \times \text{children..53 or more} - 1.90 \times \text{marital\_statusLiving with partner} \\
&+ 0.00 \times \text{marital\_statusMarried} - 2.78 \times \text{marital\_statusNever married} + 0.91 \times \text{marital\_statusSeparated} \\
&+ 1.72 \times \text{marital\_statusWidowed} - 2.40 \times \text{sleep>8hrs} - 2.37 \times \text{sleep6-8hrs} - 2.76 \times \text{raceMexican American} \\
&+ 0.14 \times \text{raceOther} - 1.98 \times \text{raceWhite} - 2.16 \times \text{snortNot recorded} \\
&- 0.57 \times \text{snortYes} - 2.33 \times \text{alcoholNo drinking} - 1.79 \times \text{alcoholNot recorded}
\end{align*}
```
### LASSO

```{=tex}
\begin{align*}
\text{sbp} = &\, 84.13 \times \text{(Intercept)} + 0.52 \times \text{bmi} + 0.79 \times \text{hdl} + 1.43 \times \text{total\_chol} + 0.04 \times \text{AST} \\
&- 0.17 \times \text{diabetesNo} + 1.88 \times \text{diabetesYes} - 14.02 \times \text{citizenship\_statusDon't Know} \\
&- 0.59 \times \text{citizenship\_statusNot a citizen of the US} - 12.06 \times \text{citizenship\_statusRefused} \\
&+ 3.09 \times \text{educ\_levelHighschool} + 2.19 \times \text{educ\_levelLess12grade} + 1.16 \times \text{educ\_levelsomeCollege} \\
&- 0.99 \times \text{children..51} - 1.17 \times \text{children..52} + 0.90 \times \text{children..53 or more} \\
&+ 4.42 \times \text{genderMale} + 0.44 \times \text{age\_yr} + 1.77 \times \text{marital\_statusLiving with partner} \\
&+ 0.01 \times \text{marital\_statusMarried} + 2.95 \times \text{marital\_statusNever married} - 1.05 \times \text{marital\_statusSeparated} \\
&+ 7.19 \times \text{marital\_statusWidowed} - 1.47 \times \text{sleep>8hrs} - 2.95 \times \text{sleep6-8hrs} \\
&- 4.11 \times \text{raceMexican American} - 3.43 \times \text{raceOther} - 5.14 \times \text{raceWhite} \\
&+ 1.75 \times \text{smokeNot Smoking} + 0.22 \times \text{smokeSmoking} - 2.74 \times \text{snortNot recorded} \\
&- 0.61 \times \text{snortYes} - 1.69 \times \text{alcoholNo drinking} - 0.28 \times \text{alcoholNot recorded} \\
&- 1.62 \times \text{income\_categoryLower-middle income} - 3.04 \times \text{income\_categoryMiddle income} \\
&- 2.64 \times \text{income\_categoryUnknown/Refused} - 2.71 \times \text{income\_categoryUpper-middle income} \\
&- 4.54 \times \text{income\_categoryVaried/High income}
\end{align*}
```
```{=tex}
\begin{align*}
\text{dbp} = &\, 47.99 + 0.24 \times \text{bmi} + 0.80 \times \text{total\_chol} + 0.58 \times \text{hemoglobin} + 0.17 \times \text{albumin} \\
&+ 0.04 \times \text{AST} - 0.42 \times \text{diabetesNo} - 3.18 \times \text{diabetesYes} + 1.36 \times \text{citizenship\_statusDon't Know} \\
&- 0.60 \times \text{citizenship\_statusNot a citizen of the US} - 1.78 \times \text{citizenship\_statusRefused} \\
&- 0.11 \times \text{educ\_levelHighschool} - 0.92 \times \text{educ\_levelLess12grade} - 0.39 \times \text{educ\_levelsomeCollege} \\
&- 0.99 \times \text{children..51} - 1.39 \times \text{children..52} - 2.08 \times \text{children..53 or more} \\
&+ 0.59 \times \text{genderMale} + 0.01 \times \text{age\_yr} - 1.77 \times \text{marital\_statusLiving with partner} \\
&+ 0.12 \times \text{marital\_statusMarried} - 2.67 \times \text{marital\_statusNever married} + 0.94 \times \text{marital\_statusSeparated} \\
&+ 1.69 \times \text{marital\_statusWidowed} + 2.21 \times \text{cycle} - 2.21 \times \text{sleep>8hrs} \\
&- 2.25 \times \text{sleep6-8hrs} - 2.08 \times \text{raceMexican American} + 0.31 \times \text{raceOther} \\
&- 2.09 \times \text{raceWhite} + 0.44 \times \text{smokeNot Smoking} + 0.75 \times \text{smokeSmoking} \\
&- 2.15 \times \text{snortNot recorded} - 0.50 \times \text{snortYes} - 1.28 \times \text{alcoholNo drinking} \\
&- 1.17 \times \text{alcoholNot recorded}
\end{align*}
```
# Discussion and conclusion
